Erosion of somatic tissue identity with loss of the X-linked intellectual disability factor KDM5C

### 2024-07-25 submission/manuscript.Rmd
discussion notes

@@

- include cancer in there somewhere (Somatic misexpression of germline genes has been implicated in many cancers.)

>>>>

- Talk about impact - Other germline gene chromatin regulators, NDDs, cancer. Maybe talk about myt1l
- include cancer in there somewhere (Somatic misexpression of germline genes has been implicated in many cancers.)

@@
